Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
Edits after pdf pass

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML and Javascript. To broaden access to customization, our prior
  work developed an approach that empowers end-users to customize
  websites without traditional programming via a browser extension
  called Wildcard. However, Wildcard only opened part of the
  customization process to end-users, and still required programmers to
  write site-specific adapters to map website data to a table structure.
  This means that end-users can only customize a website if a programmer
  has written an adapter for it. Furthermore, end-users do not have the
  ability to extend adapters in order to perform new customizations or
  repair adapters to fix broken customizations.

@@

The workflow steps are shown in Figure~\ref{fig:creating}:

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 1).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 3 and 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML and Javascript. To broaden access to customization, our prior
  work developed an approach that empowers end-users to customize
  websites without traditional programming via a browser extension
  called Wildcard. However, Wildcard only opened part of the
  customization process to end-users, and still required programmers to
  write site-specific adapters to map website data to a table view
  through which the customizations are made. This means that end-users
  can only customize a website if a programmer has written an adapter
  for it. Furthermore, end-users do not have the ability to extend
  adapters in order to perform new customizations or repair adapters to
  fix broken customizations.

@@

The system provides live feedback as Jen hovers, demonstrating the
\textbf{live programming} principle. The workflow steps are shown in
Figure~\ref{fig:creating}:

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 3).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 3 and 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}
